EuPPollNet: A European database of plant-pollinator networks

### 2024-04-17 Manuscript/EuPPollNet_Ms.qmd
edits

The interactions between different plant and pollinator species within a community form complex networks. Macro-ecological analyses of the topology of these networks have revealed common properties across them, such as truncated power-law degree distributions [@jordano1987] or nestedness [@bascompte2003], and has added relevant information of their interaction ecology of plant-pollinator networks across geographic regions [@olesen2002; @traveset2016] and environmental gradients [@ramos2010; @rech2016; @saunders2023]. Although macro-ecological approaches make significant contributions to knowledge, they tend to be rare, and are strongly influenced by the spatio-temporal availability and nature of the data [@burkle2011; @trojelsgaard2013]. For instance, plant-pollinator studies tend to differ in sampling effort and methodology which can impact the structure of the resulting plant-pollinator networks [@gibson2011; @jordano2016]. Further, despite little sampling effort could capture most of the relevant functional species [@hegland2010], most plant-pollinator networks have unobserved interactions because undersampling [@olesen2011; @chacoff2012]. Thus, the lack of strong spatio-temporal coverage along the current intrinsic limitations of sampling plant-pollinator networks, highlight the need of keep gathering and integrating informative species interaction data to properly unravel the different ecological processes that shape plant-pollinator interactions at large scales.

Here, we present the EuPPollNet database, an acronym derived from European plant-pollinator networks, which contains harmonized informative interaction data of plants and pollinators at European level. The primary focus of the pollinator taxonomic groups is on the main orders of entomofauna that visit and pollinate flowering plants in Europe. These include insect species from the orders Hymenoptera, Diptera, Lepidoptera, and Coleoptera [@potts2015], which comprise almost the totality of recorded interactions in the EuPPollNet database (`r format(round(main_orders_percent, 2), nsmall = 2)`%). To understand the scope of the database, we examine the taxonomic and sampling coverage of the different plant and pollinator species at European level with the help of the most up-to-date species checklists and rarefaction analyses. In addition, we investigate how two key structural metrics of plant-pollinator networks, such as connectance and nestedness, change across the latitudinal range of studies and bioclimatic regions. Finally, we also examine whether plant-pollinator networks fulfill the expectation of being more nested than null expectations. EuPPollNet aims to cover a wide range of taxonomic groups and habitats, while also providing other variables of interest that allow to better control for the ecological context and sampling methods. In addition, EuPPollNet offers a transparent and accessible workflow of its data management and species harmonization that allow to being reused and keep building on it over time. We expect that this database will help to evaluate macro-ecological processes and current gaps of plant-pollinator interactions at European level.

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 2}. Graphs (a-b-c) indicate the accumulation curves for pollinators, plants, and their interactions across sampling sites. Grey solid lines represent 100 randomized accumulation curves, the black solid lines represents the interpolated curve (i.e., the mean across curves), and the red dashed lines illustrates the extrapolated curve for approximately 3000 sampling sites. The solid black points indicate the number of species and interactions contained in the database. Graph (d) shows the accumulation curve of pollinator species across increasing number of plant species. This last graph uses the same color and shape structure as the ones in the top panel. Graphs (e-f) indicate the percentage of occurrence (i.e., incidence) of plant and pollinator species across sampling sites. Species on the left (i.e., common) are found in many sampling sites, while species on the right (i.e., rare) are found in few or only a single sampling site.", fig.width=10, fig.height=6, out.width="115%"}

@@

The proportion of the major pollinator orders within the database differed across habitats and bioclimatic regions (**Figure 5**). As expected, Hymenoptera was the main taxonomic order on the majority of habitats, exceeded only by Diptera on the habitat categories of riparian vegetation, moors and heathland, and alpine grasslands. Overall, the proportion of Lepidoptera and Coleoptera was low across all habitats but Coleoptera showed a notably increase in sclerophyllous vegetation and beaches, dunes and sands habitat categories. Similar patterns were observed when exploring the pollinator proportions by bioclimatic region. In this particular case, Hymenoptera was the predominant order in all bioclimatic regions with Diptera taking more importance in Alpine and Atlantic regions. Again, Lepidoptera shows low proportions across all bioclimatic regions and Coleptera seems to be only relevant in Mediterranean regions at European level. Notably, the number of studies (**Figure 5**) and sampling sites (**Figure S2**) also differs across habitats and bioclimatic regions. The habitats sampled by a higher number of studies in the database are `r studies_by_habitat$EuPPollNet_habitat[[1]]` (`r studies_by_habitat$Habitat_count[[1]]`), `r studies_by_habitat$EuPPollNet_habitat[[2]]` (`r studies_by_habitat$Habitat_count[[2]]`) and `r studies_by_habitat$EuPPollNet_habitat[[3]]` (`r studies_by_habitat$Habitat_count[[3]]`). However, the habitats that contain a higher number of sampling sites are `r networks_by_habitat$EuPPollNet_habitat[[1]]` (`r networks_by_habitat$Habitat_count[[1]]`), `r networks_by_habitat$EuPPollNet_habitat[[2]]` (`r networks_by_habitat$Habitat_count[[2]]`) and `r networks_by_habitat$EuPPollNet_habitat[[3]]` (`r networks_by_habitat$Habitat_count[[3]]`). The bioclimatic regions with a higher number of studies are `r studies_by_bioregion$Bioregion[[1]]` (`r studies_by_bioregion$Bioregion_count[[1]]`), `r studies_by_bioregion$Bioregion[[2]]` (`r studies_by_bioregion$Bioregion_count[[2]]`) and `r studies_by_bioregion$Bioregion[[3]]` (`r studies_by_bioregion$Bioregion_count[[3]]`); and the ones that contain a higher number of sampling sites are `r networks_by_bioregion$Bioregion[[1]]` (`r networks_by_bioregion$Bioregion_count[[1]]`), `r networks_by_bioregion$Bioregion[[2]]` (`r networks_by_bioregion$Bioregion_count[[2]]`) and `r networks_by_bioregion$Bioregion[[3]]` (`r networks_by_bioregion$Bioregion_count[[3]]`).

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 5}. Proportion of the major pollinator orders by habitat types and bioclimatic regions in the EuPPollNet database. The orders, from left to right, include Hymenoptera, Diptera, Lepidoptera and Coleoptera. The horizontal barplot on the right indicates the number of studies that were conducted on each habitat type or bioclimatic region. Note that a single study can countribute to more than one habitat or bioclimatic region. Areas with a greater number of studies are more likely to depict accurate proportions of the different pollinator orders in those systems.", fig.width=4.5, fig.height=8, fig.align='center'}

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 6}. Graphs (a-b) indicate network connectance and nestedness across the latitudinal range of the studies from the database. In addition, the bioclimatic region where each network is located is indicated with points of different shapes and colours. Graph (c) shows the the association between network connectances and the geometric mean of plant and pollinator species per network. Graph (d) shows the distribution of z-scores when comparing the nestedness from the empirical networks with their randomised counterparts (100 null models for each network). The vertical red dashed lines represent the z critical value for a two tailed test with alpha = 0.05. Z-scores to the left of the first vertical red dashed line indicate that networks are less nested than expected by chance (red), those between the two dashed lines indicate no statistical difference from random expectations (green), and those to the right indicate that networks are more nested than expected by chance (blue).", fig.width=10, fig.height=7, fig.align='center'}

@@

#--------------------------------------------------------------------------------------------#
p1+p2+p3 + plot_layout(guides = "collect") & 
theme(plot.title = element_text(size = 14, face = "bold"),
      axis.title = element_text(face = "bold", size = 14),
      axis.text = element_text(face = "bold", size = 14))

>>>>

The interactions between different plant and pollinator species within a community form complex networks. Macro-ecological analyses of the topology of these networks have revealed common properties across them, such as truncated power-law degree distributions [@jordano1987] or nestedness [@bascompte2003], and has added relevant information of their interaction ecology of plant-pollinator networks across geographic regions [@olesen2002; @traveset2016] and environmental gradients [@ramos2010; @rech2016; @saunders2023]. Although macro-ecological approaches make significant contributions to knowledge, they tend to be rare, and are strongly influenced by the spatio-temporal availability and nature of the data [@burkle2011; @trojelsgaard2013]. For instance, plant-pollinator studies tend to differ in sampling effort and methodology which can impact the structure of the resulting plant-pollinator networks [@gibson2011; @jordano2016]. Further, despite little sampling effort could capture most of the relevant functional species [@hegland2010], most plant-pollinator networks have unobserved interactions because of undersampling [@olesen2011; @chacoff2012]. Thus, the lack of strong spatio-temporal coverage along the current intrinsic limitations of sampling plant-pollinator networks, highlight the need to keep gathering and integrating informative species interaction data to properly unravel the different ecological processes that shape plant-pollinator interactions at large scales.

Here, we present the EuPPollNet database, an acronym derived from European plant-pollinator networks, which contains harmonized informative interaction data of plants and pollinators at European level. The primary focus of the pollinator taxonomic groups is on the main orders of entomofauna that visit and pollinate flowering plants in Europe. These include insect species from the orders Hymenoptera, Diptera, Lepidoptera, and Coleoptera [@potts2015], which comprise almost the totality of recorded interactions in the EuPPollNet database (`r format(round(main_orders_percent, 2), nsmall = 2)`%). To understand the scope of the database, we examine the taxonomic and sampling coverage of the different plant and pollinator species at European level with the help of the most up-to-date species checklists and rarefaction analyses. In addition, we investigate how two key structural metrics of plant-pollinator networks, such as connectance and nestedness, change across the latitudinal range of studies and bioclimatic regions. Finally, we also examine whether plant-pollinator networks fulfill the expectation of being more nested than null expectations. EuPPollNet aims to cover a wide range of taxonomic groups and habitats, while also providing other variables of interest that allow better control for the ecological context and sampling methods. In addition, EuPPollNet offers a transparent and accessible workflow of its data management and species harmonization that allows it to be reused and keep building on it over time. We expect that this database will help to evaluate macro-ecological processes and current gaps of plant-pollinator interactions at European level.

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 2}. Graphs (a-b-c) indicate the accumulation curves for pollinators, plants, and their interactions across sampling sites. Grey solid lines represent 100 randomized accumulation curves, the black solid lines represent the interpolated curve (i.e., the mean across curves), and the red dashed lines illustrate the extrapolated curve for approximately 3000 sampling sites. The solid black points indicate the number of species and interactions contained in the database. Graph (d) shows the accumulation curve of pollinator species across an increasing number of plant species. This last graph uses the same color and shape structure as the ones in the top panel. Graphs (e-f) indicate the percentage of occurrence (i.e., incidence) of plant and pollinator species across sampling sites. Species on the left (i.e., common) are found in many sampling sites, while species on the right (i.e., rare) are found in few or only a single sampling site.", fig.width=10, fig.height=6, out.width="115%"}

@@

The proportion of the major pollinator orders within the database differed across habitats and bioclimatic regions (**Figure 5**). As expected, Hymenoptera was the main taxonomic order on the majority of habitats, exceeded only by Diptera on the habitat categories of riparian vegetation, moors and heathland, and alpine grasslands. Overall, the proportion of Lepidoptera and Coleoptera was low across all habitats but Coleoptera showed a notably increase in sclerophyllous vegetation and beaches, dunes and sands habitat categories. Similar patterns were observed when exploring the pollinator proportions by bioclimatic region. In this particular case, Hymenoptera was the predominant order in all bioclimatic regions with Diptera taking more importance in Alpine and Atlantic regions. Again, Lepidoptera shows low proportions across all bioclimatic regions and Coleoptera seems to be only relevant in Mediterranean regions at European level. Notably, the number of studies (**Figure 5**) and sampling sites (**Figure S2**) also differs across habitats and bioclimatic regions. The habitats sampled by a higher number of studies in the database are `r studies_by_habitat$EuPPollNet_habitat[[1]]` (`r studies_by_habitat$Habitat_count[[1]]`), `r studies_by_habitat$EuPPollNet_habitat[[2]]` (`r studies_by_habitat$Habitat_count[[2]]`) and `r studies_by_habitat$EuPPollNet_habitat[[3]]` (`r studies_by_habitat$Habitat_count[[3]]`). However, the habitats that contain a higher number of sampling sites are `r networks_by_habitat$EuPPollNet_habitat[[1]]` (`r networks_by_habitat$Habitat_count[[1]]`), `r networks_by_habitat$EuPPollNet_habitat[[2]]` (`r networks_by_habitat$Habitat_count[[2]]`) and `r networks_by_habitat$EuPPollNet_habitat[[3]]` (`r networks_by_habitat$Habitat_count[[3]]`). The bioclimatic regions with a higher number of studies are `r studies_by_bioregion$Bioregion[[1]]` (`r studies_by_bioregion$Bioregion_count[[1]]`), `r studies_by_bioregion$Bioregion[[2]]` (`r studies_by_bioregion$Bioregion_count[[2]]`) and `r studies_by_bioregion$Bioregion[[3]]` (`r studies_by_bioregion$Bioregion_count[[3]]`); and the ones that contain a higher number of sampling sites are `r networks_by_bioregion$Bioregion[[1]]` (`r networks_by_bioregion$Bioregion_count[[1]]`), `r networks_by_bioregion$Bioregion[[2]]` (`r networks_by_bioregion$Bioregion_count[[2]]`) and `r networks_by_bioregion$Bioregion[[3]]` (`r networks_by_bioregion$Bioregion_count[[3]]`).

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 5}. Proportion of the major pollinator orders by habitat types and bioclimatic regions in the EuPPollNet database. The orders, from left to right, include Hymenoptera, Diptera, Lepidoptera and Coleoptera. The horizontal barplot on the right indicates the number of studies that were conducted on each habitat type or bioclimatic region. Note that a single study can contribute to more than one habitat or bioclimatic region. Areas with a greater number of studies are more likely to depict accurate proportions of the different pollinator orders in those systems.", fig.width=4.5, fig.height=8, fig.align='center'}

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 6}. Graphs (a-b) indicate network connectance and nestedness across the latitudinal range of the studies from the database. In addition, the bioclimatic region where each network is located is indicated with points of different shapes and colours. Graph (c) shows the association between network connectance and the geometric mean of plant and pollinator species per network. Graph (d) shows the distribution of z-scores when comparing the nestedness from the empirical networks with their randomised counterparts (100 null models for each network). The vertical red dashed lines represent the z critical value for a two tailed test with alpha = 0.05. Z-scores to the left of the first vertical red dashed line indicate that networks are less nested than expected by chance (red), those between the two dashed lines indicate no statistical difference from random expectations (green), and those to the right indicate that networks are more nested than expected by chance (blue).", fig.width=10, fig.height=7, fig.align='center'}

@@

#--------------------------------------------------------------------------------------------#
p1+p2+p3 + plot_layout(guides = "collect") & 
theme(plot.title = element_text(size = 14, face = "bold"),
      axis.title = element_text(face = "bold", size = 14),
      axis.text = element_text(face = "bold", size = 12))

### 2024-04-17 Manuscript/EuPPollNet_word.qmd
edits

---
title: "EuPPollNet: A European database of plant-pollinator networks"
format:
  pdf:
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
        \usepackage{caption}
        \captionsetup[figure]{labelformat=empty}
        \captionsetup[table]{labelformat=empty}

bibliography: references.bib
latex-tinytex: false
link-citations: TRUE
linkcolor: RoyalBlue
urlcolor: RoyalBlue
---

@@

#--------------------------------------------------------------------------------------------#
p1+p2+p3 + plot_layout(guides = "collect") & 
theme(plot.title = element_text(size = 14, face = "bold"),
      axis.title = element_text(face = "bold", size = 14),
      axis.text = element_text(face = "bold", size = 14))

>>>>

---
title: "EuPPollNet: A European database of plant-pollinator networks"
format:
  docx:
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
        \usepackage{caption}
        \captionsetup[figure]{labelformat=empty}
        \captionsetup[table]{labelformat=empty}

bibliography: references.bib
latex-tinytex: false
prefer-html: true
link-citations: TRUE
linkcolor: RoyalBlue
urlcolor: RoyalBlue
---

@@

#--------------------------------------------------------------------------------------------#
p1+p2+p3 + plot_layout(guides = "collect") & 
theme(plot.title = element_text(size = 14, face = "bold"),
      axis.title = element_text(face = "bold", size = 14),
      axis.text = element_text(face = "bold", size = 1))

### 2024-04-17 Manuscript/Figures_and_Tables/2_Figure_2.Rmd
edits

#Pollinators-----
poll_output = readRDS("../Data/Working_files/pollinator_sampling_coverage.rds")
pollinators_curves = readRDS("../Data/Working_files/collectors_curves_pollinators.rds")
#Create dataset
d_poll = poll_output$iNextEst$Network_id
#Check cols
d_poll$col = d_poll$method

@@

#Plants-----
plant_output = readRDS("../Data/Working_files/plant_sampling_coverage.rds")
plant_curves = readRDS("../Data/Working_files/collectors_curves_plants.rds")
#Create dataset
d_plant = plant_output$iNextEst$Network_id
#Check cols
d_plant$col = d_plant$method

@@

#Interactions-----
int_output = readRDS("../Data/Working_files/interactions_sampling_coverage.rds")
interactions_curves = readRDS("../Data/Working_files/collectors_curves_interactions.rds")
#Create dataset
d_int = int_output$iNextEst$Network_id
#Check cols
d_int$col = d_int$method

@@

#----------------#
#Pollinators
#----------------#
#Read data
data = readRDS("../Data/Working_files/Interactions_uncounted.rds")%>% 
mutate(Network_id = paste0(Study_id, Network_id))  
#First select cols of rank, accepted name and study ID
#Then select unique levels by study ID
#Now sum levels (maximum can be as maximum number of studies)
poll_spread = data %>% 
select(Pollinator_rank, Pollinator_accepted_name, Network_id) %>% 
group_by(Network_id) %>% 
filter(Pollinator_rank == "SPECIES") %>% 
distinct(Pollinator_accepted_name) %>% 
ungroup() %>% 
count(Pollinator_accepted_name) %>% 
rename(n_networks_shared = n) %>% 
arrange(-n_networks_shared) %>% 
mutate(Percent_total = n_networks_shared / n_distinct(data$Network_id))

@@

#Pollinator by plant species
plant_poll_curves = readRDS("../Data/Working_files/collectors_curves_plant_ploll.rds")
plant_poll_output = readRDS("../Data/Working_files/plant_poll_spp_sampling_coverage.rds")

>>>>

#Pollinators-----
poll_output = readRDS("../../Data/Working_files/pollinator_sampling_coverage.rds")
pollinators_curves = readRDS("../../Data/Working_files/collectors_curves_pollinators.rds")
#Create dataset
d_poll = poll_output$iNextEst$Network_id
#Check cols
d_poll$col = d_poll$method

@@

#Plants-----
plant_output = readRDS("../../Data/Working_files/plant_sampling_coverage.rds")
plant_curves = readRDS("../../Data/Working_files/collectors_curves_plants.rds")
#Create dataset
d_plant = plant_output$iNextEst$Network_id
#Check cols
d_plant$col = d_plant$method

@@

#Interactions-----
int_output = readRDS("../../Data/Working_files/interactions_sampling_coverage.rds")
interactions_curves = readRDS("../../Data/Working_files/collectors_curves_interactions.rds")
#Create dataset
d_int = int_output$iNextEst$Network_id
#Check cols
d_int$col = d_int$method

@@

#----------------#
#Pollinators
#----------------#
#Read data
data = readRDS("../../Data/Working_files/Interactions_uncounted.rds")%>% 
mutate(Network_id = paste0(Study_id, Network_id))  
#First select cols of rank, accepted name and study ID
#Then select unique levels by study ID
#Now sum levels (maximum can be as maximum number of studies)
poll_spread = data %>% 
select(Pollinator_rank, Pollinator_accepted_name, Network_id) %>% 
group_by(Network_id) %>% 
filter(Pollinator_rank == "SPECIES") %>% 
distinct(Pollinator_accepted_name) %>% 
ungroup() %>% 
count(Pollinator_accepted_name) %>% 
rename(n_networks_shared = n) %>% 
arrange(-n_networks_shared) %>% 
mutate(Percent_total = n_networks_shared / n_distinct(data$Network_id))

@@

#Pollinator by plant species
plant_poll_curves = readRDS("../../Data/Working_files/collectors_curves_plant_ploll.rds")
plant_poll_output = readRDS("../../Data/Working_files/plant_poll_spp_sampling_coverage.rds")

### 2024-04-17 Manuscript/Figures_and_Tables/3_Figure_3.Rmd
edits

#Read data
tree_family_interactions= readRDS("../Data/Manuscript_info/bee_phylo.RData")
d1 = readRDS("../Data/Manuscript_info/bee_data.RData")
n = readRDS("../Data/Manuscript_info/node_data.RData")

>>>>

#Read data
tree_family_interactions= readRDS("../../Data/Manuscript_info/bee_phylo.RData")
d1 = readRDS("../../Data/Manuscript_info/bee_data.RData")
n = readRDS("../../Data/Manuscript_info/node_data.RData")

### 2024-04-17 Manuscript/Figures_and_Tables/4_Figure_4.Rmd
edits

library(ggplot2)
library(ggtree)
library(ggnewscale)
library(ggtreeExtra)
library(viridis)
#Save data and plot it in an Rmarkdown
tree_family_interactions = readRDS("../Data/Manuscript_info/plant_phylo.RData")
d1 = readRDS("../Data/Manuscript_info/plant_coverage_phylo_RData")

>>>>

library(ggplot2)
library(ggtree)
library(ggnewscale)
library(ggtreeExtra)
library(viridis)
#Save data and plot it in an Rmarkdown
tree_family_interactions = readRDS("../../Data/Manuscript_info/plant_phylo.RData")
d1 = readRDS("../../Data/Manuscript_info/plant_coverage_phylo_RData")

### 2024-04-17 Manuscript/Figures_and_Tables/6_Figure_6.Rmd
edits

# Load libraries
library(dplyr)
library(ggplot2)
library(stringr)
library(patchwork)
library(psych)
# Load data
data = readRDS("../Data/3_Final_data/Interaction_data.rds")
metrics_by_network = readRDS("../Data/Working_files/metrics_by_network.rds")
null_networks = readRDS("../Data/Working_files/null_networks.rds")
null_metrics_networks = readRDS("../Data/Working_files/null_metrics_networks.rds")

>>>>

# Load libraries
library(dplyr)
library(ggplot2)
library(stringr)
library(patchwork)
library(psych)
# Load data
data = readRDS("../../Data/3_Final_data/Interaction_data.rds")
metrics_by_network = readRDS("../../Data/Working_files/metrics_by_network.rds")
null_networks = readRDS("../../Data/Working_files/null_networks.rds")
null_metrics_networks = readRDS("../../Data/Working_files/null_metrics_networks.rds")

### 2024-04-17 Manuscript/Figures_and_Tables/Figure_S1.Rmd
edits

#Load libraries
library(dplyr)
library(readr)
library(viridis)
library(ggplot2)
#--------------------------------------------------------------------------------------------#
#Start from bees----
#Load data
#Safenet interactions
data = readRDS("../Data/3_Final_data/Interactions_uncounted.rds")
#Bee-syrphid Masterlist
master_list = read_csv("../Data/Species_taxonomy/Thesaurus/Master_bees_syrphids.csv")
#Load butterfly masterlist
master_list1 <- read.delim(file = "../Data/Species_taxonomy/Thesaurus/Butterfly_taxon.txt",
                    header = T)
#Bee families
bee_fam = c("Apidae", "Megachilidae", "Halictidae", 
            "Andrenidae", "Colletidae","Melittidae")

>>>>

#Load libraries
library(dplyr)
library(readr)
library(viridis)
library(ggplot2)
#--------------------------------------------------------------------------------------------#
#Start from bees----
#Load data
#Safenet interactions
data = readRDS("../../Data/3_Final_data/Interactions_uncounted.rds")
#Bee-syrphid Masterlist
master_list = read_csv("../../Data/Species_taxonomy/Thesaurus/Master_bees_syrphids.csv")
#Load butterfly masterlist
master_list1 <- read.delim(file = "../../Data/Species_taxonomy/Thesaurus/Butterfly_taxon.txt",
                    header = T)
#Bee families
bee_fam = c("Apidae", "Megachilidae", "Halictidae", 
            "Andrenidae", "Colletidae","Melittidae")
